\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref}


\begin{document}
{\Large \textbf{Victor Elgersma}} 
\vspace{0.1cm} % Add vertical space

\hrule 
\vspace{0.1cm} % Add vertical space

\href{mailto:elgersmav@gmail.com}{elgersmav@gmail.com} 


\subsection*{Education}
    \begin{flushleft}
        \hspace{1cm}\textbf{New College, University of Oxford}, \textit{Oxford, United Kingdom.} \\
        \hspace{1cm}{B.A. Physics, 2022, \textit{First Class}.} \\
    \end{flushleft}

    \begin{flushleft}
        \hspace{1cm}\textbf{European School of Brussels IV}, \textit{Brussels, Belgium.} \\
        \hspace{1cm}{European Baccalaureate, 2018} \\
    \end{flushleft}

\subsection*{Employment}

\begin{flushleft}
    \hspace{1cm}\textbf{Graduate Software Engineer}, \textit{THG Ingenuity.} \\
    \hspace{1cm}\hangindent=1cm Front-end web development of e-commerce storefronts using GraphQL, AstroJS and React. \\
    \hspace{1cm}{\textit{April 2024 - current}} \\
\end{flushleft}

\begin{flushleft}
    \hspace{1cm}\textbf{Graduate Software Engineer - Accelerator}, \textit{THG Ingenuity.} \\
    \hspace{1cm}\hangindent=1cm 6 month bootcamp designed to transition non-computer science graduates into tech. Learned object-oriented programming in Python and Java, version control, HTTP, APIs and REST, querying databases, and frontend web development using HTML, CSS, JavaScript, TypeScript, and React \\
    \hspace{1cm}\textit{{September 2023 - April 2024}} \\
\end{flushleft}

\begin{flushleft}
    \hspace{1cm}\textbf{Media Production Assistant}, \textit{The Institute of Art and Ideas.} \\
    \hspace{1cm}\hangindent=1cm {{Edited videos for DOKBOX, IAI.TV and the IAI YouTube channel. Edited podcasts for the Philosophy in Our Times series. On-set film crew during the HowTheLightGetsIn festival.   }} \\
    \hspace{1cm}\textit{{March 2023 - September 2023}} \\
\end{flushleft}

\begin{flushleft}
    \hspace{1cm}\textbf{Media Production Trainee}, \textit{The Institute of Art and Ideas.} \\
    \hspace{1cm}\textit{{January 2023 - March 2023}} \\
\end{flushleft}

\begin{flushleft}
    \hspace{1cm}\textbf{Research Assistant}, \textit{National Institute for Space Research, São Paulo, Brazil.} \\
    \hspace{1cm}\hangindent=1cm  {Worked on a hydrological model of the root water uptake in the Amazon rainforest.} \\
    \hspace{1cm}\textit{{July 2021 - August 2021}} \\
\end{flushleft}

\begin{flushleft}
    \hspace{1cm}\textbf{English Teacher}, \textit{MaiDan Summer School, Lishui, Zhejiang, China.} \\
    \hspace{1cm}\hangindent=1cm  {Taught students aged 7-14 and obtained a TEFL qualification.} \\
    \hspace{1cm}\textit{{July 2019 - August 2019}} \\
\end{flushleft}

\subsection*{Awards}

\begin{flushleft}
    \hspace{1cm}\hangindent=1cm \textbf{Scholarship, New College, University of Oxford}, for excellent exam performance in year 2; entitled to wear the Scholar's Gown, July 2020. \\
\end{flushleft}
\begin{flushleft}
    \hspace{1cm}\hangindent=1cm \textbf{Winner, PsycShorts 2019, American Psychological Association} for \textit{Behavioral Economics and the Endowment Effect}, May 2019. \\
\end{flushleft}
\begin{flushleft}
    \hspace{1cm}\hangindent=1cm \textbf{Finalist, Breakthrough Junior Challenge 2018} for \textit{Quantum Mechanics and the Wave-particle duality of matter}, September 2018. \\
\end{flushleft}
\begin{flushleft} 
    \hspace{1cm}\hangindent=1cm \textbf{Highest Academic Achievement in the English Language Section}, European School of Brussels IV, July 2018. \\
\end{flushleft}


\end{document}